Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-10-13 paper/main.tex
corrections in discussion of group results

% AO stimulus cluster location
Group results of the AO stimulus' primary contrast yielded spatially
concise / restricted clusters in the anterior part of the PPA group overlap
taken from \citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
model a hemodynamic responses but modeled from on- to offset of single words
that cue the listener about the movie's missing visual content.
% conclusion
Our group results suggest that auditory spatial information does not just
modulate activity in the PPA (depending on other factors like familiarity; s.
\citep{aziz2008modulation}) but correlates with bilaterally increased
activation.\todo{``modulate'' suggests causation}

% no task in Epstein
An early block-design study \citep{epstein1998ppa} compared results from a
paradigm that employed a (perceptual) judgment task of static pictures to a to
the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but we are still different
Nevertheless, our paradigm still differs from previous studies because the
relevant stimulus features were incidentally embedded in a continuous auditory
stream.
% conclusion
This embeddedness prevents participants from making assumptions about the
investigated perceptual process by just being exposed to the paradigm and thus
mimics experiencing the world outside the lab more closely.
% concluding statement: kinda automatic process
The lack of a task further suggests verbal spatial information is processed in
the PPA in an automatic fashion and does not necessarily rely on deliberately
paying attention to spatial information.

\paragraph{shortcomings of AO contrasts}
% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% cateogries in primary contrasts
In the current study's primary contrast, we compared verbal cues regarding
landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
scene) and elements defining the geometry of a room/locale (\texttt{groom}) to
non-spatial cues.
% we did not choose se\_new and se\_old
Notably, we did not choose the categories that contained switches from one
setting to another (texttt{se\_new} and texttt{se\_old}) which one might assume
to contain the auditory equivalent to the ``optimal'' visual stimulus type.
% why not se\_new or se\_old
These categories were actually heterogeneous: they rarely contained whole (but
also vague) descriptions of landscapes (e.g. ``in a football stadium'',
``Forrest is running through the jungle''), mostly landmarks or buildings,
and they also contained non-spatial cues.\todo{repeat examples from method
section}.
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if categories of vague verbal descriptions of a landscape as a whole
lead to differential hemodynamic activity in the PPA compared to more concrete
spatial cues.

\subsubsection{AV stimulus}
% location
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPAs from anterior to posterior and
expand into retrosplenial regions.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex)\todo{which of these regions overlap
with group ROI? which regions show clusters but do not overlap with PPA?}
% confound of higher perception
This can be attributed to the fact that we averaged the content of individual
frames after a cut and did not control for confounding features like depicted
faces or objects.
% confounds of lower perception
It further suggest low-level visual features were not averaged out leading to
clusters spanning the intracalcarine cortex.
% further studies
Hence, further studies focusing on visual perception should annotate and model
visual features of naturalistic stimuli more rigorously.
\todo[inline]{concluding statement regarding AV vs AO and cross-modality of results?}

>>>>

% AO stimulus cluster location
Group results of the AO stimulus' primary contrast yielded spatially
concise / restricted clusters in the anterior part of the PPA group overlap
taken from \citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
model hemodynamic responses but modeled from on- to offset of single words
that cue the listener about the movie's missing visual content.
% conclusion
Our group results suggest that auditory spatial information does not just
modulate activity in the PPA (depending on other factors like familiarity; s.
\citep{aziz2008modulation}) but correlates with bilaterally increased
activation.\todo{``modulate'' suggests causation}

% transition to task topic
Moreover unlike most previous studies, our paradigm was free of any task.
%
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a (perceptual) judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but we are still different
Our paradigm still differs from previous studies because the relevant stimulus
features were incidentally embedded in a continuous auditory stream.
% conclusion
This embeddedness prevents participants from making assumptions about the
investigated perceptual process by just being exposed to the paradigm and thus
mimics experiencing the world outside the lab more closely.
% concluding statement: kinda automatic process
The lack of a task further suggests verbal spatial information is processed in
the PPA in an automatic fashion and does not necessarily rely on deliberately
paying attention to spatial information.

\paragraph{shortcomings of AO contrasts}

\todo[inline]{cf. Methods: annotation \& Methods: AO copes}
% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% cateogries in primary contrasts
In the current study's primary contrast, we compared verbal cues regarding
landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
scene) and elements defining the geometry of a room/locale (\texttt{groom}) to
non-spatial cues.
% we did not choose se\_new and se\_old
Notably, we did not choose the categories that contained switches from one
setting to another (texttt{se\_new} and texttt{se\_old}) which one might assume
to contain the auditory equivalent to the ``optimal'' visual stimulus type.
% why not se\_new or se\_old
These categories were actually heterogeneous: they rarely contained whole (and
thus vague) descriptions of landscapes (e.g. ``in a football stadium'',
``Forrest is running through the jungle'') but mostly landmarks or buildings,
and also non-spatial cues.\todo{repeat examples from method section}.
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if categories of wholistic but vague verbal descriptions of
landscapes correlate with differential hemodynamic activity in the PPA compared
to more concrete spatial cues.

\subsubsection{AV stimulus}
% location
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPAs from anterior to posterior and
expand into retrosplenial regions.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex)\todo{which of these regions overlap
with group ROI? which regions show clusters but do not overlap with PPA?}
% confound of higher perception
This can be attributed to the fact that we averaged the content of individual
frames after a cut and did not control for confounding features like depicted
faces or objects.
% confounds of lower perception
It further suggest low-level visual features were not averaged out leading to
clusters spanning the intracalcarine cortex.
% further studies
Since the capability to isolate clusters or networks correlating with specific
perceptual (or cognitive) processes is influenced by the amount of annotated
stimulus features further studies focusing on visual perception should annotate
and model visual features of naturalistic stimuli more rigorously.\todo{ouf,
okay...}
% cross-modal control purpose?
\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
results?}
